Parameterized convection, grid-scale clouds and resolution sensitivity in the Community Atmosphere Model

### 2019-08-08 resolution.tex
edits

\cite{RETAL2016CD} derive an estimate $n= b-1$ by combining a scale analysis of the continuity equation with a power law representation $\Delta x^{2b}$ of the second-order structure function of the horizontal wind. Strictly speaking, $\Delta x$ here refers to the distance between two points for which the velocity increment is computed in the structure function, but with this distance set to the model grid-spacing. Observations indicate that $b=\frac{1}{3}$ for scales less than about $1000$ km \citep{CETAL1999JGR}, which according to the Weiner–Khinchin theorem $- \left( 2b+1 \right) = -\frac{5}{3}$ is equal to the slope of the kinetic energy spectrum for mesoscale motions \citep{NG1985JAS}. \cite{RETAL2016CD} argue that the $-\frac{5}{3}$ slope is common in both observations and models, and provides an emergent constraint for $b=\frac{1}{3}$ and $n= -\frac{2}{3}$.

>>>>

\cite{RETAL2016CD} derive an estimate $n= b-1$ by combining a scale analysis of the continuity equation with a power law representation $\Delta x^{2b}$ of the second-order structure function of the horizontal wind. Strictly speaking, $\Delta x$ here refers to the distance between two points for which the velocity increment is computed in the structure function, but with this distance set to the model grid-spacing. Observations indicate that $b=\frac{1}{3}$ for scales less than about $1000$ km \citep{CETAL1999JGR}, which according to the Weiner–Khinchin theorem $- \left( 2b+1 \right) = -\frac{5}{3}$ is equal to the slope of the kinetic energy spectrum, which is true for observations of mesoscale flow \citep{NG1985JAS}. \cite{RETAL2016CD} argue that the $-\frac{5}{3}$ slope being common in both observations and models, provides an emergent constraint for $b=\frac{1}{3}$ and $n= -\frac{2}{3}$.
